Multiple Linear Regression on Sleep Data

### 2025-05-08 paper/paper.qmd
kable

knitr::kable(test_model_stats, caption = "MLR Outcome for")
```

@@

```{r}
sleep_test_final <- sleep_test_vif %>%
  dplyr::select(!c(gender, occupation, bmi_category, sleep_disorder, daily_steps))

model_final <- lm(sleep_duration ~., sleep_test_final)
summary(model_final)
```

>>>>

knitr::kable(test_model_stats, caption = "MLR Outcome for age and quality of sleep removed")
```

@@

```{r}
sleep_test_final <- sleep_test %>%
  dplyr::select(!c(gender, occupation, bmi_category, sleep_disorder, daily_steps))

final_model <- lm(sleep_duration ~., sleep_test_final)
final_model_summary <- summary(model_final)

final_model_stats <- tibble::tibble(`F-statistic` = round(final_model_summary$fstatistic[1], 2),
                              `Adjusted R²` = round(final_model_summary$adj.r.squared, 3),
                              `Residual Sum of Squares` = round(sum(residuals(final_model)^2), 2),
                              `Total Sum of Squares` = round(sum((sleep_test_final$sleep_duration-mean(sleep_test_final$sleep_duration))^2), 2))

knitr::kable(final_model_stats, caption = "Final Model Statistics")
```
